Kindly Bent to Free Us

### 2019-07-08 kindly/intro.tex
minor cosmetics

Most type systems provide just type soundness, but neglect the
protocol aspect. The systems that do build on linear types \cite{Girard} and/or
uniqueness types\cite{DBLP:conf/plilp/BarendsenS95}. A value of linear
type is guaranteed to be consumed 
exactly once. That is, a file that has been opened must be closed and
memory that has been allocated must be released. A value of unique
type is guaranteed to have a single reference to it.

@@

\begin{itemize}
\item Type system that encodes linearity and affinity with borrowing
\item Full type inference for \dots
\item Constraint simplification
\item Automatic inference of regions for borrows
\end{itemize}

>>>>

Most type systems provide just type soundness, but neglect the
protocol aspect. The systems that do build on linear types \cite{DBLP:journals/tcs/Girard87} and/or
uniqueness types\cite{DBLP:conf/plilp/BarendsenS95}. A value of linear
type is guaranteed to be consumed 
exactly once. That is, a file that has been opened must be closed and
memory that has been allocated must be released. A value of unique
type is guaranteed to have a single reference to it.

@@

\begin{itemize}
\item A type system that encodes linearity and affinity with
  borrowing. The type system is polymorphic with respect to types as
  well as kinds that express constraint on the number of uses of a value.
\item An extension of the HM(X) framework
  \cite{DBLP:journals/tapos/OderskySW99} with kinds, regions, and
  multiplicity constraints that supports full, prinicipal type inference.
\item Constraint simplification techniques.
\item Automatic inference of regions for borrows.
\end{itemize}
